GEE models

### 2017-07-20 doc/esm-methods.Rmd
updated esm methods with more info on gee

Generalized estimating equations (GEE) is analogous to mixed effects models, 
except it emphasizes population-level trends over individual-level trends that 
mixed models use. Because it can handle autocorrelations in the outcome (as 
would be seen in variables measured over time), GEE modeling is well suited to
longitudinal data. Latent class mixed models (LCMM) is a form of mixed effects
modeling that tries to categorize individuals into groups that have similar
clusters; in the case of the present analysis are the trajectories in beta-cell
function over time. Because mixed models use the participant as the random
effect, LCMM can identify individuals who similarly change over time.

>>>>

Generalized estimating equations (GEE) is a technique similar to mixed effects 
modeling, except it calculates the marginal population estimates compared to the
subject-specific estimates in mixed effects models. GEE is well suited to and
commonly used in longitudinal cohort studies, especially given its capacity to
handle missed visits. GEE is able to handle longitudinal data due to the
estimating of a working correlation matrix, which was chosen based on
quasi-likelihood information criteria (QIC). The auto-regressive of order 1
(AR1) matrix was chosen for the GEE models as it had the best model fit accessed
using QIC, though other matrices (eg. exchangeable) had similar fit (data not
shown).

For the confounders, they were chosen based on previous literature, from 
directed acyclic graph (DAG) recommendations, and from QIC. The DAG
recommendations were obtained from using the DAGitty software,
http://dagitty.net/. The final GEE model selected as best fitting was negligibly
different when using insulin sensitivity or beta-cell function as an outcome and
as such the same covariates were chosen for models with each of the outcomes.
